### 2020-02-24 ChapterBackground/chapterBackground.tex
Updated: Intro to Online Gaming and extra subsections

\section{Online Gaming}
In this section an overview of online gaming challenges and system architectures will be discussed.

The main challenges facing online gaming are consistency, latency, fault-tolerance, fairness, cheating, and scalability.

@@

%TODO: Mention delta-update techniques, advantages and problems created

>>>>

\section{Online Gaming}
%TODO: Change to include related work will be discussed
In this section an overview of online gaming challenges and architectures will be discussed. 
The main challenges facing online gaming are consistency, latency, fault-tolerance, fairness, cheating, and scalability. The purpose  of this study is to demonstrate scalability and consistency of real-time physics through the use of a distributed server architecture, therefore in the following section we will define consistency with respect to online gaming and discuss existing work addressing it. Additionally Fault-tolerance, fairness and cheating will also be briefly explained, although they are not the main focus of this study, this is intended to make the reader aware of the challenges different architectures address. 
Existing work into scalability in online gaming will discussed leading into discussion of online gaming architectures. Finally, important aspects of online gaming that are relevant to this study are discussed.

@@

\subsection{Delta-Update}
%TODO: Mention delta-update techniques, advantages and problems created

\subsection{Dead-Reckoning}

\subsection{Protocols}
